The \dealii{} Library, Version 9.0

### 2018-04-05 9.0/paper.tex
Extend the list of changes.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Matthias Maier
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}
%
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
%
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

@@

@@

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation
under Award No. EAR-0949446 and EAR-1550901 and The University of California -- Davis, and National Science Foundation grant DMS-1522191.
%
% M.~Kronbichler was partially supported by the German Research Foundation (DFG)
% under the project ``High-order discontinuous Galerkin for the exa-scale''
% (ExaDG) within the priority program ``Software for Exascale Computing''
% (SPPEXA), grant agreement no.~KR4661/2-1, the Bayerisches Kompetenznetzwerk
% f\"ur Technisch-Wissenschaftliches Hoch- und H\"ochstleistungsrechnen
% (KONWIHR), and the Gauss Centre for Supercomputing e.V.~by providing computing
% time on the GCS Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ)
% through project id pr83te.
%
% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
% B.~Turcksin: This material is based upon work supported by the U.S. Department of
% Energy, Office of Science, under contract number DE-AC05-00OR22725.
%
%
% D.~Wells was supported by the National Science Foundation (NSF) through Grant
% DMS-1344962.

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

@@

\item
  Significant extension of matrix-free capabilities, including support for face integrals in discontinuous Galerkin schemes, a new Hermite-like polynomial basis adapted to face integrals that involve derivatives of shape functions, and several performance enhancements

@@

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation
under Award No. EAR-0949446 and EAR-1550901 and The University of California -- Davis, and National Science Foundation grant DMS-1522191.

M.~Kronbichler was partially supported by the German Research Foundation (DFG)
under the project ``High-order discontinuous Galerkin for the exa-scale''
(ExaDG) within the priority program ``Software for Exascale Computing''
(SPPEXA), grant agreement no.~KR4661/2-1 and the Bayerisches Kompetenznetzwerk
f\"ur Technisch-Wissenschaftliches Hoch- und H\"ochstleistungsrechnen
(KONWIHR).

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
% B.~Turcksin: This material is based upon work supported by the U.S. Department of
% Energy, Office of Science, under contract number DE-AC05-00OR22725.
%
%
% D.~Wells was supported by the National Science Foundation (NSF) through Grant
% DMS-1344962.
